---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# surveymeta

<!-- badges: start -->
<!-- badges: end -->

Surveymeta is an API client package for the [NADA API](https://catalog.ihsn.org/api-documentation/catalog/#), allowing users to retrieve survey metadata from the International Household Survey Network (IHSN) central data catalog and other repositories following the NADA standard, such as the [World Bank micro data library](https://microdata.worldbank.org/index.php/home).

## Installation

You can install the development version of surveymeta from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("northeastloon/surveymeta")
```

## Example

List surveys from 2015-2018:

```{r eval=FALSE}
library(surveymeta)

get_metadata("http://catalog.ihsn.org/index.php/api/catalog", from =2015, to = 2018, ps =ie4, var_meta = FALSE)

```


Or all metadata files created during January 2023:

```{r eval=FALSE}

get_metadata("http://catalog.ihsn.org/index.php/api/catalog", created = "2023/01/01-2023/01/31", ps =ie4, var_meta = FALSE)

```

specify `var_meta` as `TRUE` to extract variable metadata for (five) surveys


```{r eval=FALSE}
get_metadata("http://catalog.ihsn.org/index.php/api/catalog", created = "2023/01/01-2023/01/31", ps =5, var_meta = TRUE)

```
